Figures

### 2025-07-12 code/08_figures-tables.Rmd
push to continue on laptop

data_coordinates<-data.frame(Location = unique(dataset_analysis$Location),
                             Lat_Location=c(51.50,38.41,40.45,
                                            45.40,52.39, 37.18,
                                            54,39.05,
                                            51.57,48,42.54,39.95,
                                            40.13,28.10,52.06,60.39),
                             Long_Location=c(19.29,-9.02,-3.50,
                                             -64.10,6.05,-3.11,
                                             -124,-76.81,
                                             -2.26,11,8.91,-75.16,
                                             -8.27,107.10,8.25,5.32))

@@

## Count how many times each Location appears in the full dataset
location_counts <- dataset_analysis %>%
  group_by(Location) %>%
  summarise(size.freq = n_distinct(paper_ID), .groups = 'drop')

@@

# Merge the counts into the unique rows dataset
dataset_analysis_unique_rows <- dataset_analysis_unique_rows %>%
  left_join(location_counts, by = "Location")

@@

# create world map using ggplot() function 
# geom_map() function takes world coordinates as input to plot world map 
fig_map <- ggplot(world_coordinates, aes(x = long, y = lat)) + 
  geom_map(map = world_coordinates, 
    aes(map_id = region), 
    color = "white", fill= "#D9EAF7") + 
  geom_point(data = dataset_analysis_unique_rows, 
             aes(x = Long_Location, y = Lat_Location,
                 size = size.freq, colour=bird_species), alpha = 0.6) +
scale_size(range = c(3, 5)) +
  scale_fill_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +

  scale_colour_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  guides(size = "none", alpha = "none") +
  labs(x = "Longitude",
       y = "Latitude",
       col = "Bird Species")+
  theme_classic() +
  theme(legend.position = c(0.99, 0.15),
        legend.justification = c("right", "bottom"),
        legend.background = element_rect(fill = "white", color = "black"),
        legend.text = element_text(size=6),
        axis.title = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_blank())

# To add the zoomed in map.. to show the points more clearly
zoom_map <- ggplot() + 
  geom_map(data = world_coordinates, map = world_coordinates,
           aes(map_id = region),
           color = "white", fill = "#D4D4D4") +
  geom_point(data = dataset_analysis_unique_rows,
             aes(x = Long_Location, y = Lat_Location,
                 size = size.freq, colour = bird_species),
             alpha = 0.6) +
  scale_size(range = c(1, 2)) +
  scale_colour_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  coord_cartesian(xlim = c(-120, 120), ylim = c(25, 65)) +  # Northern Hemisphere
  theme_void() +
  theme(
    legend.position = "none",
    plot.background = element_rect(color = "white", fill="white"),
    panel.border = element_rect(colour = "black", fill = NA, size = 1)
  )

geographic_distribution <- ggdraw() +
  draw_plot(fig_map) +
  draw_plot(zoom_map, x = 0.10, y = 0.12, width = 0.52, height = 0.22) + theme(panel.border = element_rect(colour = "black", fill=NA, size=1.5))

@@

# Plot for lnRR
intercept_lnRR_plot <- orchaRd::orchard_plot(intercept_lnRR,
                                    mod = "1",
                                    group = "paper_ID",
                                    trunk.size = 0.25,
                                    branch.size = 2,
                                    twig.size = 0.5,
                                    alpha = 0.2,
                                    xlab = "Effect size (Log Response Ratio- lnRR)",
                                    fill = T) +
   scale_fill_manual(values = "#98C127") +
   scale_colour_manual(values = "#98C127" ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0),
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Plot for SMDH
intercept_SMDH_plot <- orchaRd::orchard_plot(intercept_SMDH,
                                    mod = "1",
                                    group = "paper_ID",
                                    trunk.size = 0.25,
                                    branch.size = 2,
                                    twig.size = 0.5,
                                    alpha = 0.2,
                                    xlab = "Effect size (Standardized Mean Difference- SMD(H))",
                                    fill = TRUE) +
  scale_fill_manual(values = "#F47A00") +
  scale_colour_manual(values = "#F47A00") +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

@@

ggsave(here::here("figures/Figure_overall_effect.png"), plot = Figure_intercept, height = 150, width = 170, units = "mm", dpi = 600)
```

@@

lnRR_hypothesis_plot <-
  orchard_plot(mod_results(lnRR_hypothesis,
                           mod = "Hypothesis",
                           group = "paper_ID"),
               trunk.size = 0.25,
               branch.size = 1,
               twig.size = 0.5,
               alpha = 0.4,
               xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "lnRR")+
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 90, vjust = 0.01, hjust = 0.5)
  )+ scale_x_discrete(labels = c("Both","Courtship","Parental Care"))

@@

SMDH_hypothesis_plot <-
  orchard_plot(
    mod_results(
      SMDH_hypothesis,
      mod = "Hypothesis",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.4,
    xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "SMD(H)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 90, vjust = 0.8, hjust = 1)
  )+ scale_x_discrete(labels = c("Both","Courtship","Parental Care"))

@@

ggsave(here::here("figures/Figure_hypothesis.png"), plot = Figure_hypothesis, height = 120, width = 250, units = "mm", dpi = 600)
```

@@

lnRR_time_gnm_addition_plot <-
  orchard_plot(mod_results(
      lnRR_time_gnm_addition,
      mod = "time_of_gnm_addition",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
 scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "lnRR")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "bottom",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  ) + scale_x_discrete(labels = c("After egg laying", "Before egg laying", "Continous addition"))

SMDH_time_gnm_addition_plot <-
  orchard_plot(mod_results(
      SMDH_time_gnm_addition,
      mod = "time_of_gnm_addition",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
 scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "SMD(H)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "bottom",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  )

@@

lnRR_design_plot <-
  orchard_plot(mod_results(
      lnRR_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
 scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "lnRR")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0),
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  ) + scale_x_discrete(labels = c("Non-aromatic Vs. Aromatic","No material Vs. Aromatic", "No material Vs. Non-Aromatic"))

SMDH_design_plot <-
  orchard_plot(mod_results(
      SMDH_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
 scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "SMD(H)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0),
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  )

>>>>

data_coordinates<-data.frame(Location = unique(dataset_analysis$Location),
                             Lat_Location=c(51.50,38.41,40.45,
                                            45.40,52.39, 37.18,40.53,
                                            54,39.05,
                                            51.57,48,42.54,39.95,
                                            40.13,28.10,52.06,60.39),
                             Long_Location=c(19.29,-9.02,-3.50,
                                             -64.10,6.05,-3.11,-4.01,
                                             -124,-76.81,
                                             -2.26,11,8.91,-75.16,
                                             -8.27,107.10,8.25,5.32))

@@

## Count how many times each Location appears in the full dataset
location_counts <- dataset_analysis %>%
  group_by(Location, bird_species) %>%
  summarise(
    size.freq = n(),
  )

@@

# Merge the counts into the unique rows dataset
dataset_analysis_unique_rows <- dataset_analysis_unique_rows %>%
  left_join(location_counts, by = c("Location", "bird_species"))

@@

# create world map using ggplot() function 
# geom_map() function takes world coordinates as input to plot world map 
fig_map <- ggplot(world_coordinates, aes(x = long, y = lat)) + 
  geom_map(map = world_coordinates, 
    aes(map_id = region), 
    color = "white", fill= "#D9EAF7") + 
  geom_point(data = dataset_analysis_unique_rows, 
             aes(x = Long_Location, y = Lat_Location,
                 size = size.freq, colour=bird_species),
             alpha = 0.6) +
 scale_size(range = c(1, 2.5)) +
  scale_fill_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +

  scale_colour_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  guides(size = "none", alpha = "none",
         colour = guide_legend(override.aes = list(size = 1.5), keywidth = 0.4,
                               keyheight = 0.4))+
  labs(x = "Longitude",
       y = "Latitude",
       col = "Bird Species")+
  theme_classic() +
  theme(plot.margin = margin(t =15, r = 15, b = 5, l = 5),  
        legend.position = c(1.02, 0.42),
        legend.justification = c("right", "bottom"),
        legend.background = element_rect(fill = "white", color = "black"),
        legend.text = element_text(size=6),
        legend.title = element_text(size=7),
        axis.title = element_text(size = 8),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10))

# To add the zoomed in map.. to show the points more clearly
zoom_map <- ggplot() + 
  geom_map(data = world_coordinates, map = world_coordinates,
           aes(map_id = region),
           color = "white", fill = "#D4D4D4") +
  geom_point(data = dataset_analysis_unique_rows,
             aes(x = Long_Location, y = Lat_Location,
                 size = size.freq, colour = bird_species),
             position = position_jitter(width = 0.2, height = 0.2),
             alpha = 0.7) +
  scale_size(range = c(1, 2)) +
  scale_colour_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  coord_cartesian(xlim = c(-10, 20), ylim = c(25, 65)) +  # Northern Hemisphere
  theme_void() +
  theme(
    legend.position = "none",
    plot.background = element_rect(color = "white", fill="white"),
    panel.border = element_rect(colour = "black", fill = NA, size = 1)
  )

geographic_distribution <- ggdraw() +
  draw_plot(fig_map) +
  draw_plot(zoom_map, x = 0.11, y = 0.21, width = 0.20, height = 0.28) + theme(panel.border = element_rect(colour = "black", fill=NA, size=1.2))

@@

# Plot for lnRR

intercept_lnRR_plot<- orchaRd::orchard_plot(intercept_lnRR,
                                             mod = "1",
                                             group = "paper_ID",
                                             trunk.size = 0.3,
                                             branch.size = 2,
                                             twig.size = 0.5,
                                             alpha = 0.2,
                                             xlab = "Effect size (lnRR)", 
                                             fill =  T,
                                             k.pos = c(0.53,0.6,0.6)) +
  scale_fill_manual(values = "#98C127") +
  scale_colour_manual(values = "#98C127" ) +
theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0),
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Plot for SMDH
intercept_SMDH_plot <- orchaRd::orchard_plot(intercept_SMDH,
                                    mod = "1",
                                    group = "paper_ID",
                                    trunk.size = 0.3,
                                    branch.size = 2,
                                    twig.size = 0.5,
                                    alpha = 0.2,
                                    xlab = "Effect size (SMDH)",
                                    fill = TRUE,
                                    k.pos = c(2,0.6,0.6)) +
  scale_fill_manual(values = "#F47A00") +
  scale_colour_manual(values = "#F47A00") +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

@@

ggsave(here::here("figures/Figure_overall_effect.png"), plot = Figure_intercept, height = 150, width = 170, units = "mm", dpi = 600)

###----------------------------------------------------------------------------------

## Now the cropped versions presented in the main manuscript..

###----------------------------------------------------------------------------------

intercept_lnRR_plot_crop <- orchaRd::orchard_plot(intercept_lnRR,
                                             mod = "1",
                                             group = "paper_ID",
                                             trunk.size = 0.5,
                                             branch.size = 2,
                                             twig.size = 0.5,
                                             alpha = 0.2,
                                             xlab = "Effect size (lnRR)", 
                                             fill =  T,
                                             k.pos = c(0.53,0.6,0.6)) +
  scale_fill_manual(values = "#98C127") +
  scale_colour_manual(values = "#98C127" ) +
    scale_y_continuous(limits = c(-0.6, 0.6)) +
theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0),
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Plot for SMDH
intercept_SMDH_plot_crop <- orchaRd::orchard_plot(intercept_SMDH,
                                    mod = "1",
                                    group = "paper_ID",
                                    trunk.size = 0.5,
                                    branch.size = 2,
                                    twig.size = 0.5,
                                    alpha = 0.2,
                                    xlab = "Effect size (SMDH)",
                                    fill = TRUE,
                                    k.pos = c(2,0.6,0.6)) +
  scale_fill_manual(values = "#F47A00") +
  scale_colour_manual(values = "#F47A00") +
  scale_y_continuous(limits = c(-2.3, 2.3)) +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Combine using patchwork
Figure_intercept_crop <- intercept_lnRR_plot_crop / intercept_SMDH_plot_crop +
  plot_annotation(tag_level = c("A","B"))

ggsave(here::here("figures/Figure_overall_effect_crop.png"), plot = Figure_intercept_crop, height = 150, width = 170, units = "mm", dpi = 600)
```

@@

lnRR_hypothesis_plot <-
  orchard_plot(mod_results(lnRR_hypothesis,
                           mod = "Hypothesis",
                           group = "paper_ID"),
               trunk.size = 0.25,
               branch.size = 1,
               twig.size = 0.5,
               alpha = 0.4,
               xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "Effect size (lnRR)")+
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Both","Courtship","Parental Care"))

@@

SMDH_hypothesis_plot <-
  orchard_plot(
    mod_results(
      SMDH_hypothesis,
      mod = "Hypothesis",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.4,
    xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "Effect size (SMDH)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Both","Courtship","Parental Care"))

@@

ggsave(here::here("figures/Figure_hypothesis.png"), plot = Figure_hypothesis, height = 120, width = 250, units = "mm", dpi = 600)

##-----------------------------------------------------------------------------

# Now the cropped figures for the main manuscript

##-----------------------------------------------------------------------------

lnRR_hypothesis_plot_crop <-
  orchard_plot(mod_results(lnRR_hypothesis,
                           mod = "Hypothesis",
                           group = "paper_ID"),
               trunk.size = 0.5,
               branch.size = 1.3,
               twig.size = 0.5,
               alpha = 0.4,
               fill = T,
               k.pos = c(0.4,0.6,0.6),
               xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
    scale_y_continuous(limits = c(-0.6, 0.6)) +
  labs(x = "",
       y = "Effect size (lnRR)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 5),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Both","Courtship","Parental\nCare"))

SMDH_hypothesis_plot_crop <-
  orchard_plot(
    mod_results(
      SMDH_hypothesis,
      mod = "Hypothesis",
      group = "paper_ID"
    ),
    trunk.size = 0.5,
    branch.size = 1.3,
    twig.size = 0.5,
    alpha = 0.4,
    fill = T,
    k.pos = c(1.9,0.6,0.6),
    xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_y_continuous(limits = c(-2.3, 2.3)) +
  labs(x = "",
       y = "Effect size (SMDH)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 5),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Both","Courtship","Parental\nCare"))

SMDH_hypothesis_plot_crop <- SMDH_hypothesis_plot_crop +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

# Combine using patchwork
Figure_hypothesis_crop <- lnRR_hypothesis_plot_crop + SMDH_hypothesis_plot_crop +
  plot_annotation(tag_level = c("A","B"))

ggsave(here::here("figures/Figure_hypothesis_crop.png"), plot = Figure_hypothesis_crop, height = 120, width = 250, units = "mm", dpi = 600)
```

@@

lnRR_time_gnm_addition_plot <-
  orchard_plot(mod_results(
    lnRR_time_gnm_addition,
    mod = "time_of_gnm_addition",
    group = "paper_ID"
  ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(0.4,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "Effect Size (lnRR)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
        legend.position.inside = c(0.99, 0.01),
        legend.justification = c(1, 0), 
        legend.direction = "horizontal",
        legend.background = element_blank(),
        legend.key = element_blank(),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 6),
        axis.title = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  ) + scale_x_discrete(labels = c("After egg\nlaying", "Before egg\nlaying", "Continous\naddition"))

SMDH_time_gnm_addition_plot <-
  orchard_plot(mod_results(
    SMDH_time_gnm_addition,
    mod = "time_of_gnm_addition",
    group = "paper_ID"
  ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(0.4,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794"))+
  labs(x = "",
       y = "Effect Size (SMDH)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
        legend.position.inside = c(0.99, 0.01),
        legend.justification = c(1, 0), 
        legend.direction = "horizontal",
        legend.background = element_blank(),
        legend.key = element_blank(),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 6),
        axis.title = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  ) + scale_x_discrete(labels = c("After egg\nlaying", "Before egg\nlaying", "Continous\naddition"))

##-----------------------------------------------------------------------------

# Now the cropped figures for the main manuscript

##-----------------------------------------------------------------------------

lnRR_time_gnm_addition_plot_cropped <-
  orchard_plot(mod_results(
    lnRR_time_gnm_addition,
    mod = "time_of_gnm_addition",
    group = "paper_ID"
  ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(0.4,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_y_continuous(limits = c(-0.6, 0.6)) +
  labs(x = "",
       y = "Effect Size (lnRR)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
        legend.position.inside = c(0.99, 0.01),
        legend.justification = c(1, 0), 
        legend.direction = "horizontal",
        legend.background = element_blank(),
        legend.key = element_blank(),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 6),
        axis.title = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  ) + scale_x_discrete(labels = c("After egg\nlaying", "Before egg\nlaying", "Continous\naddition"))

SMDH_time_gnm_addition_plot_cropped <-
  orchard_plot(mod_results(
      SMDH_time_gnm_addition,
      mod = "time_of_gnm_addition",
      group = "paper_ID"
    ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
    k.pos = c(1.9,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_y_continuous(limits = c(-2.3, 2.3)) +
labs(x = "",
     y = "Effect Size (SMDH)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  ) + scale_x_discrete(labels = c("After egg\nlaying", "Before egg\nlaying", "Continous\naddition"))

@@

lnRR_design_plot <-
  orchard_plot(mod_results(
      lnRR_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(1,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
labs(x = "",
     y = "Effect Size (lnRR)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. Aromatic","No material\nVs. Aromatic", "No material\nVs. Non-Aromatic"))

SMDH_design_plot <-
  orchard_plot(mod_results(
      SMDH_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(1.5,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794"))+
labs(x = "",
     y = "Effect Size (SMDH)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. Aromatic","No material\nVs. Aromatic", "No material\nVs. Non-Aromatic"))

##-----------------------------------------------------------------------------

# Now the cropped figures for the main manuscript

##-----------------------------------------------------------------------------

lnRR_design_plot_cropped <-
  orchard_plot(mod_results(
      lnRR_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(0.4,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_y_continuous(limits = c(-0.6, 0.6)) +
labs(x = "",
     y = "Effect Size (lnRR)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. Aromatic","No material\nVs. Aromatic", "No material\nVs. Non-Aromatic"))
